Software Citation Principles

### 2016-03-17 sc-principles/software-citation-principles.tex
updating the discussion on UIDs

\textbf{Unique identifiers} \katznote{Is this discussion topic needed?  I would like to delete it.}

A UID points to a specific software, but multiple UIDs might point to the same software.
\LJHnote{not sure that multiple UIDs would be a recommended best practice as  this could cause conflicts} \katznote{LJH: not recommended, but likely will happen anyhow} \katznote{maybe discuss how identifiers are created}

>>>>

\textbf{Unique identifiers}

The ``unique'' in a UID means that it points to a unique, specific software. However, multiple UIDs might point to the same software.  This is not recommended, but is possible.  We strongly recommend that if there is already a UID for a version of software, no additional UID should be
created.  Multiple UIDs can lead to split credit, which does not help anyone.  In particular, we
urge the use of standard DOIs as the UIDs for software.

%\LJHnote{not sure that multiple UIDs would be a recommended best practice as  this could cause conflicts} \katznote{LJH: not recommended, but likely will happen anyhow} \katznote{maybe discuss how identifiers are created}
